Analysis of transit delays in the Toronto Transit Commission: 2024

### 2024-09-24 paper/paper.qmd
Update paper.qmd

---
title: "My title"
author: 
  - Dong Jun Yoon
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analysis of transit delays in the Toronto Transit Commission: 2024"
author: 
  - Dong Jun Yoon
thanks: "Code and data are available at: https://github.com/DJY1231/TTC-report-2024.git"
date: today
date-format: long
abstract: "This paper analyzes TTC delay data to understand patterns and causes of delays. It finds buses experience the most delays, especially on certain routes, while subways have frequent undocumented delays. Mechanical issues, operations, and diversions are most common delay causes. The analysis indicates the need to reduce bus delays through more vehicles or tactics like bus bridging on certain routes."
format: pdf
number-sections: true
bibliography: references.bib
